---
title: "Figure S1 Collection Locations"
author: "Talia_Karasov"
date: "5/21/2019"
output: html_document
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figs/',
                      echo=FALSE, warning=FALSE, message=FALSE)
```

```{r}
library(ggmap)
library(ggsn)
library(maps)
library("rnaturalearth")
library("rnaturalearth")
library("sf")
library(sp)
library("ggspatial")
#plot locations of collections
```

```{r}
plot_region <- function(locations, city_size, nudge = 0.05){
  #ne_rivers <- ne_download(scale = 50, type = 'rivers_lake_centerlines', category = 'physical')
#sp::plot(rivers50)
  data(world.cities)
  world.cities <- world.cities[world.cities$pop>city_size,]
  coordinates(world.cities) <- ~long+lat 
  proj4string(world.cities) <- '+init=epsg:4326'
  cities_fin = data.frame(name = world.cities$name, coordinates(world.cities))
  world <- ne_countries(scale = "medium", returnclass = "sf")
class(world)
  height = max(locations$Latitude) - min(locations$Latitude) 
  width = max(locations$Longitude) - min(locations$Longitude)
  borders = c(bottom = min(locations$Latitude) - 0.2 * height, 
            top = max(locations$Latitude) + 0.2 * height,
            left = min(locations$Longitude) - 0.2 * width,
            right = max(locations$Longitude) + 0.2 * width)
  #river.subset = river.subset <- quick.subset(ne_rivers, borders)

  p1 = ggplot(data = world) +
    geom_sf() +
    annotation_scale(location = "bl", width_hint = 0.5) +
    #annotation_north_arrow(location = "bl", which_north = "true", pad_x = unit(0.75, "in"), pad_y = unit(0.5, "in"), style = north_arrow_fancy_orienteering) +
    coord_sf(xlim = c(borders['left'], borders['right']), ylim = c(borders['bottom'], borders['top'])) +
    geom_point(data = locations, mapping = aes(x = Longitude, y = Latitude), color = "#FF5A0088", cex = 3) +
    theme_bw() +
  geom_point(data = data.frame(cities_fin), aes(x=long, y=lat), col='grey40', pch=20, cex=1) +
    geom_text(data=cities_fin, aes(x=long, y=cities_fin$lat, label=cities_fin$name), hjust = 0, nudge_x = nudge, color = "grey40") 
  # +  geom_path(data=river.subset, aes(x = long, y = lat, group = group), color = 'blue')
  return(p1)
  }
```

Germany
```{r}
locations=read.table("~/Dropbox/germany_pathogen_collections/data_files_rmarkdown/location_sampling_lat_long.txt",header=T)

pdf("~/Dropbox/controlled_metagenomics/results_figures/german1_map_7_2019.pdf", useDingbats = FALSE, family = "ArialMT")
plot_region(locations, 10000, nudge = 0.01)
dev.off()

```

But we also need a zoomed out German
```{r}
data(world.cities)
city_size = 100000
world.cities <- world.cities[world.cities$pop>city_size,]
coordinates(world.cities) <- ~long+lat 
proj4string(world.cities) <- '+init=epsg:4326'
cities_fin = data.frame(name = world.cities$name, coordinates(world.cities))
world <- ne_countries(scale = "medium", returnclass = "sf")
class(world)
height = max(locations$Latitude) - min(locations$Latitude) 
width = max(locations$Longitude) - min(locations$Longitude)
borders = c(bottom = 47.3, 
            top = 49,
            left = 7.5,
            right = 10)
  #river.subset = river.subset <- quick.subset(ne_rivers, borders)
p_overall = ggplot(data = world) +
    geom_sf() +
    annotation_scale(location = "bl", width_hint = 0.5) +
    #annotation_north_arrow(location = "bl", which_north = "true", pad_x = unit(0.75, "in"), pad_y = unit(0.5, "in"), style = north_arrow_fancy_orienteering) +
    coord_sf(xlim = c(borders['left'], borders['right']), ylim = c(borders['bottom'], borders['top'])) +
    theme_bw() +
  geom_point(data = data.frame(cities_fin), aes(x=long, y=lat), col='grey40', pch=20, cex=1) +
    geom_text(data=cities_fin, aes(x=long, y=cities_fin$lat, label=cities_fin$name), hjust = 0, nudge_x = 0.05, color = "grey40") 

pdf("~/Dropbox/controlled_metagenomics/results_figures/german1_overall_7_2019.pdf", useDingbats = FALSE, family = "ArialMT") 
p_overall 
dev.off()
```

Sweden
```{r}
#sweden
locations=read.table("~/Dropbox/controlled_metagenomics/Swedish_samples/swedish_sites.txt",header=T, sep="\t")

pdf("~/Dropbox/controlled_metagenomics/results_figures/swedish1_map_7_2019.pdf", useDingbats = FALSE, family = "ArialMT")
plot_region(locations, 500000)
dev.off()
```








DEPRECATED BELOW!

scalebar = function(x,y,w,n,d, units="km"){
  # x,y = lower left coordinate of bar
  # w = width of bar
  # n = number of divisions on bar
  # d = distance along each division
  
  bar = data.frame( 
    xmin = seq(0.0, n*d, by=d) + x,
    xmax = seq(0.0, n*d, by=d) + x + d,
    ymin = y,
    ymax = y+w,
    z = rep(c(1,0),n)[1:(n+1)],
    fill.col = rep(c("black","white"),n)[1:(n+1)])
  
  labs = data.frame(
    xlab = c(seq(0.0, (n+1)*d, by=d) + x, x), 
    ylab = c(rep(y+w*1.5, n+2), y+3*w),
    text = c(as.character(seq(0.0, ((n+1)*d)/1000, by=d/1000)), units)
  )
  list(bar, labs)
}

#germany
locations=read.table("~/Dropbox/germany_pathogen_collections/data_files_rmarkdown/location_sampling_lat_long.txt",header=T)
sb = scalebar(x = 9.05, y = 48.45, w = 0.005, n = 3 , 0.0143, "km" )

pdf("~/Dropbox/germany_pathogen_collections/data_files_rmarkdown/locations_collections.pdf")

#qmplot(Longitude, Latitude, data = locations, extent = "panel", mapcolor = "bw", maptype = "toner")+geom_point(color="RED", cex=4)+geom_rect(data=sb[[1]], aes(xmin=xmin, xmax=xmax, ymin=ymin, ymax=ymax, fill=z), inherit.aes=F, show.legend = F,  color = "black", fill = sb[[1]]$fill.col)+geom_text(data=sb[[2]], aes(x=xlab, y=ylab, label=text), inherit.aes=F, show.legend = F) 

#the above code is working poorly
height = max(locations$Latitude) - min(locations$Latitude) 
width = max(locations$Longitude) - min(locations$Longitude)
borders = c(bottom = min(locations$Latitude) - 0.1 * height, 
            top = max(locations$Latitude) + 0.1 * height,
            left = min(locations$Longitude) - 0.1 * width,
            right = max(locations$Longitude) + 0.1 * width)

map = get_stamenmap(borders, zoom = 10, maptype = "toner-lite")
ggmap(map) +
  geom_point(data = locations, mapping = aes(x = Longitude, y = Latitude), color = "RED", cex = 4) +
  geom_rect(data=sb[[1]], aes(xmin=xmin, xmax=xmax, ymin=ymin, ymax=ymax, fill=z), inherit.aes=F, show.legend = F,  color = "black", fill = sb[[1]]$fill.col)+geom_text(data=sb[[2]], aes(x=xlab, y=ylab, label=text), inherit.aes=F, show.legend = F) 

dev.off()

#sweden
locations=read.table("~/Dropbox/controlled_metagenomics/Swedish_samples/swedish_sites.txt",header=T, sep="\t")
sb = scalebar(17, 56, 0.5, n = 5, 1, "km" )

pdf("~/Dropbox/controlled_metagenomics/results_figures/swedish_map2.pdf", useDingbats = FALSE)
#qmplot(Longitude, Latitude, data = locations, extent = "panel")+geom_point(color="RED", cex=4)+geom_rect(data=sb[[1]], aes(xmin=xmin, xmax=xmax, ymin=ymin, ymax=ymax, fill=z), inherit.aes=F, show.legend = F,  color = "black", fill = sb[[1]]$fill.col)+geom_text(data=sb[[2]], aes(x=xlab, y=ylab, label=text), inherit.aes=F, show.legend = F) 



#the above code is working poorly
height = max(locations$Latitude) - min(locations$Latitude) 
width = max(locations$Longitude) - min(locations$Longitude)
borders = c(bottom = min(locations$Latitude) - 0.1 * height, 
            top = max(locations$Latitude) + 0.1 * height,
            left = min(locations$Longitude) - 0.9 * width,
            right = max(locations$Longitude) + 0.9 * width)

map = get_stamenmap(borders, zoom = 6, maptype = "toner-lite")
hm = get_map(borders, zoom = 6, source = "stamen",
             maptype = "toner") 
ggmap(map, extent = "device") +
  geom_point(data = locations, mapping = aes(x = Longitude, y = Latitude), color = "RED", cex = 4)  +
  theme_bw()

#Scale bar not working well
#+scalebar(data = locations, transform = TRUE, dist_unit = "km", dist = 1)
  
  
  #geom_rect(data=sb[[1]], aes(xmin=xmin, xmax=xmax, ymin=ymin, ymax=ymax, fill=z), inherit.aes=F, show.legend = F,  color = "black", fill = sb[[1]]$fill.col)+geom_text(data=sb[[2]], aes(x=xlab, y=ylab, label=text), inherit.aes=F, show.legend = F) 

dev.off()
```